Millions of Type Errors

### 2023-04-03 oopsla23/paper.tex
Lite -> Impersonal
redo dataset overview, add brief comments

\title{Millions of Type Errors}
\subtitle{Lite Telemetry to Measure User Experience}
% lean, lite, modest, non-intrusive, private, ...

@@

    \code{IncorrectGenericParameterCount} & Arity mismatch for a generic type \\
    \code{CountMismatch} & \FILL{} \\
    \code{UnknownProperty} & Referenced an invalid field or method  \\
    \code{OnlyTablesCanHaveMethods} & Tried to attach a method to a non-table \\
    \code{CannotCallNonFunction} & Called a value that is not a function \\
    \code{TypesAreUnrelated} & Failed to cast, unify, or check subtyping \\
    \code{TypeMismatch} & Generic label for other type errors \\
    \code{GenericError}
    & Generic label for other errors, e.g., declaring a \\
    & supertype that is not a class type
    %% or iterated over a table without specifying how

@@

\begin{table}[t]
  \caption{Dataset overview}
  \label{t:dataset-overview}
\begin{tabular}{rl}
 5,108 & total logs \\
       & 4,574 nocheck + 510 nonstrict + 24 strict \\
 182,247 & total forced strict type errors \\
       & {113,274 in module, 6,425 in edit regions} \\
  1,521 & total type errors \\
       & {1,485 in module, 331 in edit regions}
  \\[2ex]

  1,146 & sessions \\
  & \begin{tabular}{rl}
      1,143 & single mode = 1046 nocheck + 94 nonstrict + 3 strict \\
      7 & multi mode projects \\
      3 & mode upgrades \\
      4 & mode downgrades
    \end{tabular}
\end{tabular}
\end{table}

@@

>>>>

\title{Millions of Type Errors}
\subtitle{Impersonal Telemetry to Measure User Experience}
% lean, lite, modest, non-intrusive, private, ...

@@

    \code{IncorrectGenericParameterCount} & Arity mismatch for a generic type \\
    \code{CountMismatch} & \FILL{} \\
    \code{UnknownProperty} & Referenced an invalid field or method  \\
    \code{OnlyTablesCanHaveMethods} & Tried to attach a method to a non-table \\
    \code{CannotCallNonFunction} & Called a value that is not a function \\
    \code{TypesAreUnrelated} & Failed to cast, unify, or check subtyping \\
    \code{TypeMismatch} & Generic label for other type errors \\
    \code{GenericError}
    & Generic label for other errors, e.g., declaring a \\
    & \quad{} supertype that is not a class type
    %% or iterated over a table without specifying how

@@

\begin{figure}[t]
\begin{tabular}{rl}
 5108 total logs = 4574 nocheck + 510 nonstrict + 24 strict
 182247 total forced strict type errors, 83005 in module, 5113 in edit regions
 1521 total type errors, 1035 in module, 110 non-stx + 47 syntax in edit regions
 1146 sessions
  1143 single mode = 1046 nocheck + 94 nonstrict + 3 strict
  2 multi mode projects
  2 mode upgrades
  2 mode downgrades

 5,108 & total logs \\
       & 4,574 nocheck + 510 nonstrict + 24 strict \\
 182,247 & total forced strict type errors \\
       & {83,005 in module, 5,113 in edit regions} \\
  1,521 & total type errors \\
       & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
  \\[2ex]

  1,146 & sessions \\
  & \begin{tabular}{l}
      1,143 single mode = 1046 nocheck + 94 nonstrict + 3 strict \\
      detected 2 multi-mode projects, 2 mode upgrades, 2 mode downgrades
    \end{tabular}
\end{tabular}
  \caption{Dataset overview}
  \label{f:dataset-overview}
\end{figure}

\Cref{f:dataset-overview}:
cannot filter syntax errors from the total and per-module error counts (\cref{s:threats});
multi-mode project = found a module switch that coincides with a mode switch, which suggests that two modules have different modes;
upgrade = found a up-mode switch that does not match a module switch (quite possible to miss these);
downgrade = found a down-mode switch that does not match a module switch

@@

\section{Threats to Validity}
\label{s:threats}

Error counts per-project and per-module include syntax errors.
Problematic, because syntax errors are uninteresting (easy to fix),
but common, which makes it likely that our per-keystroke telemetry will record them.
Edit region has specific counts.
Next time, we should do that for the other aggregates.
